---
title: "CANDEV DATA CHALLENGE"
subtitle: "TEAM 2571"
author: "HIMANSHU GARG, KAUSTUBH DUTTA, RAJ, PRINCE"
date: "`r Sys.time()`"
output: 
  html_document:
    theme: cerulean
    highlight: tango
    code folding: hide
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: true

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r include=FALSE}
my_data<- read.csv("data.csv")
my_data
```

# Manufacturing sales, by industry for 12 Selected Census Metropolitan Areas


```{r echo=FALSE}
Aero <- which(my_data$North.American.Industry.Classification.System..NAICS.=="Aerospace product and parts manufacturing [3364]")
#print(my_data$GEO[Aero]) 
#print(my_data$VALUE[Aero])
```

**The Aerospace product and parts manufacturing [3364] got a peak in MARCH 2019 and a dip in JULY 2019**


**Province having the Maximum revenue in Aerospace manufacturing in 10 Years among 12 metropolitan cities**

### 
```{r echo=FALSE}
MAX_AERO<- my_data$GEO[Aero][which.max(my_data$VALUE[Aero])]
MAX_AERO
```

**Annual Sales Value Average over 10 years of Aerospace Product and Parts Manufacturing in Region in the last 10 years**

```{r echo=FALSE}
sum(my_data$VALUE[Aero][which(my_data$GEO[Aero]==MAX_AERO)])
```

**Minimum revenue of Aero in 10 Years"**

```{r echo=FALSE}
MIN_AERO<- my_data$GEO[Aero][which.min(my_data$VALUE[Aero])]
MIN_AERO
```

**Annual Avg over 10 years revenue of Aero in Region with minimum annual avg**
```{r echo=FALSE}
sum(my_data$VALUE[Aero][which(my_data$GEO[Aero]==MIN_AERO)])
```

**When was the Maximum revenue of Aero generated in 10 Years**
```{r echo=FALSE}
MAX_MONTH<- my_data$REF_DATE[Aero][which.max(my_data$VALUE[Aero])]
MAX_MONTH
```
# Sales Trend over years
```{r echo=FALSE}
library(ggplot2)
plot(my_data$GEO[Aero],my_data$VALUE[Aero])
```



